\opt{ant,tea,it}{\section*{\education}

\begin{itemize}

\opt{ant,tea}{
  \item \phd \inside \anthropology, Goldsmiths College, University of London, 2013.
\opt{ant}{
  \begin{itemize}
    \item \textit{\doctorthesis:}
      Nicaraguan Sandinismo, Back from the Dead? An anthropological study of popular participation within the Frente Sandinista de Liberación Nacional
    \item \textit{\supervisor:}
      Dr Stephen Nugent.
    \end{itemize}
}
}
\opt{ant,tea}{
  \item \ma \inside \history, \malmouni, 2019.
\opt{ant}{
  \begin{itemize}
    \item \textit{\masterthesis:}
      Nationalization of electricity and oil in core and periphery: Norway versus Mexico
    \item \textit{\supervisor:}
      Dr. Mats Greiff
    \end{itemize}
}
  \item \mphil \inside \socialanthropology, \uio, 2006.
\opt{ant}{
  \begin{itemize}
    \item \textit{\masterthesis:}
      Defining the Territory. What Community do US Americans in a Border Town to Mexico belong to?
    \item \textit{\supervisor:}
      Dr. Polit. Geir Thomas Hylland Eriksen.
    \end{itemize}
}

  \item \bachelor \inside \history, \uio, 2007.
\opt{tea}{
  \begin{itemize}
    \item \textit{\including:}
      \english \und \geography
  \end{itemize}}
  \item \bachelor \inside \socialanthropology, \uio, 2003.
\opt{tea}{
    \begin{itemize}
      \item \textit{\including:}
        \sociology \opt{nono}{\und \philosophy}
    \end{itemize}}
}
\opt{it}{
  \item HBX CORe, Harvard Business School, Honors, 2015.
}
\opt{tea}{
  \item \teachingcredentials \ppu, \uio, 2006.
    \begin{itemize}
      \item \textit{\fagdidaktikk:}
        \english, \history \und \socialsciences
    \end{itemize}
  }

\end{itemize}

}

\opt{tea,ant}{
\section*{\certification}
\begin{itemize}
  \item \textit{Copyright for Multimedia}
    Duke University, Emory University \& The University of North Carolina at Chapel Hill, Coursera, 2016.
  \item \textit{J4SC101x: Journalism for Social Change},
    University of California, Berkeley, edX, 2016.
  \item \textit{Ebola: Essential Knowledge for Health Professionals},
    University of Amsterdam \und Utrecht University, Coursera, 2015.
  \item \textit{Advanced Security in the Field (ASITF)},
    United Nations Department of Safety and Security, 2014.
  \item \textit{Basic Security in the Field II (BSITF II)},
    United Nations Department of Safety and Security, 2014.
  \item \textit{Herramientas Digitales para el Periodismo de Datos}\opt{en,de,no,dk}{ (\english: Digital Tools for Data Journalism)},
    Knight Center for Journalism in the Americas, University of Texas at Austin, 2014.
  \opt{tea}{
    \item \textit{Fantasy and Science Fiction: The Human Mind, Our Modern World},
      University of Michigan, Coursera, 2013.
    \item \textit{Cambridge Certificate in English Language Teaching to Adults},
      Cambridge University / International House Barcelona, 2007.
  }

\end{itemize}
}
