
\section*{\individuallectures}

\begin{itemize}

\item \March 2014: \opt{en,no,dk,de}{"A comparison of the question of lands during the first part of the current Nicaraguan government under Daniel Ortega (2006--11) and the government of Fernando Lugo (2008-12) in Paraguay"}\opt{es}{"Una comparación la cuestion de tierras durante la primera etapa del gobierno actual de Daniel Ortega en Nicaragua (2006--11) y el gobierno de Fernando Lugo en Paraguay (2008--12)"}, Anarchist Book Fair, Oakland, California, \USA.

\item \March 2014: \opt{en,no,dk,de}{"How do Bitcoins work?", (\spanish: }¿Cómo funcionan los bitcoins?\opt{en,no,dk,de}{)}, Ministerio de la Juventud, Managua, Nicaragua.

\item \February 2014: \opt{en,no,dk,de}{"How do avoid internet spying", (\spanish: }Como evadir el espionaje online\opt{en,no,dk,de}{)}, Encuentro de los jóvenes comunicadores del departamento de León, León, Nicaragua.

\item \February 2014: \opt{en,no,dk,de}{"International Data security in the age of the NSA", (\spanish: }Seguridad de datos a nivel internacional en la edad de la NSA\opt{en,no,dk,de}{)}, Primer Encuentro Latinoamericano sobre Juventud, Tecnologia, e Inovación, Managua, Nicaragua.

\item \December 2013: "Semantic editing with Fidus Writer"\opt{es}{ (\spanish: Cómo y por qué editar en forma semantica con Fidus Writer)}, \opt{no,dk,en}{talk and workshop, Leibniz Institute for the Social Sciences (GESIS), Cologne}\opt{es}{charla y taller, Instituto de las Ciencias Sociales Leibniz (GESIS), Colonia}\opt{de}{Vortrag/Oberseminar, 
GESIS - Leibniz-Institut für Sozialwissenschaften, Köln}, \Germany.

\item \October 2013: "How can science be moved to the web?"\opt{es}{ (\spanish: ¿Cómo mover la ciencia al internet?)}, workshop, Mozilla Festival, London.  

\item \October 2012: "Revolutionen, Staatstreiche und Soziale Bewegungen in Latein Amerika" (\english: Revolutions, coup d'etats and social movemenets in Latin America\opt{es}{, \spanish: Revoluciones, golpes de estados y movimientos sociales en América Latina}), 3 \days \series, AStA, Hochschule Darmstadt University of Applied Sciences, \Germany.
	\begin{itemize}
	\item "Nicaragua und seine Revolutionen und was ist der Sandinismus heute" (\english: Nicaragua and its revolutions and what is Sandinismo today\opt{es}{, \spanish: Nicaragua y sus revoluciones y lo que es el Sandinismo hoy en día}).
	\item "Die Staatsstreiche in Honduras und Paraguay, ein Vergleich" (\english: The coup d'etats of Honduras and Paraguay, a comparison\opt{es}{, \spanish: Una comparación entre los golpes de estados en Honduras y Paraguay}).
	\item "Soziale Bewegungen und deren Einfluss, der Fall der autonomen Stadt Oaxaca im Herbst 2006" (\english: Social movements and their influence, the case of the autonomous city of Oaxaca, Fall 2006\opt{es}{, \spanish: Movimientos sociales y su influencia, el caso de la ciudad autónoma de Oaxaca, otoño 2006}).
	\end{itemize}


\item \August 2012: "Zur Macht per Wahl und entfernt per Staatstreich" (\english: Taking power through elections and being removed through coup d'etats\opt{es}{, \spanish: Tomar el poder tras elecciones y perderlo a traves de un golpe de estado}), workshop, Solid Sommercamp 2012, Kratzeburg, \Germany.

\item \March 2012: "Nicaragua – Is the country developing?"\opt{es}{ (\spanish: Nicaragua – ¿Está desarrollando el país?)}, presentation/discussion, Fundación La Isla, León, Nicaragua.

\item \March 2012: "Las diferentes licencias de Software Libre" (\english: The different licences of free software), Festival Nacional de Software Libre, UNI, Nicaragua.

\item \March 2012: "Is Nicaragua developing"\opt{es}{ (\spanish: ¿Está desarrollando Nicaragua?)}, presentation/discussion, Casa Tres Mundos, Tipitapa, Nicaragua.

\item \March 2012: "Periodismo en el contexto internacional" (\english: Journalism in an international context), lecture for students of \emph{letras y filologia}, UNAN-Managua, Nicaragua.

\item \March 2012: "Nicaragua – On Sandinismo and development strategies"\opt{es}{ (\spanish: Nicaragua – Sobre el Sandinismo y estrategias de desarrollo)}, half-day seminar, Casa del Tercer Mundo, Estelí, Nicaragua.

\item \March 2012: "PIPA, SOPA y ACTA\ldots y que significan para nosotros en Nicaragua" (\english: PIPA, SOPA, ACTA\ldots and what they mean for us in Nicaragua), Foro-debate nacional sobre las Redes Sociales, UNAN-Managua, Nicaragua.

\item \March 2012: "Alternativas de Facebook y Twitter" (\english: Alternatives to Facebook and Twitter), Foro-debate nacional sobre las Redes Sociales, UNAN-Managua, Nicaragua.

\item \February 2012: "Nicaragua – Is the Revolution still alive"\opt{es}{ (\spanish: Nicaragua – ¿Está viva la revolución?)}, presentation/discussion, Revolutionary Grounds Coffee Shop, Tucson, Arizona, \USA.

\item \December 2010: "Non-indigenous people in the Amazon – or why anthropologists like to exotify", Lowland South America course, Goldsmiths College, London, \UK.

\item \October 2010: "The agricultural information system ALBAstryde – Experiences with development by using the Internet in Nicaragua", Google UK Creative Lab, London, \UK.

\item \September 2010: "ALBAstryde - un sistema para el socialismo del siglo 21" (\english: ALBAstryde - a system for the socialism of the 21st century), Centro de Ingeniería Genética y Biotecnología, Habana, Cuba.

\item \August 2010: "Linke und soziale Bewegungen in Lateinamerika" (\english: Leftist and social movements in Latin America), Solid Sommercamp 2010, Porstendorf b/Jena, \Germany.

\item \April 2010: "Revolution und Konterrevolution in Zentralamerika" (\english: Revolution and Counterrevolution in Central America), Linkes Pfingstcamp 2010, Brandenburg, \Germany.

\item \June 2010: "Symbolism in the Honduran resistance movement", London Anthropology Day, SOAS, \UK.

\item \September 2009: "Albastryde - como combinar politicas visionarias y software libre" (\english: Albastryde – how to combine visionary politics with open source software) Día Debian 2009, UPOLI, Managua, Nicaragua.

\item \April 2009: "Use de bases de datos" (\english: Usage of database systems), FADCANIC directorial board, Bluefields, Nicaragua.

\item \August 2008: "Latex - ¿para qué nos sirve la software libre en aspectos de publicaciones?" (\english: Latex - what good does open source software do us in publishing?) Día Debian 2008, UNI, Managua, Nicaragua.
\end{itemize}


\section*{\teachingexperience}

\begin{itemize}
\item \Fall 2010 – \Spring 2011: Visiting tutor for Anthropology course "Lowland South America", Goldsmiths College, University of London, \UK.

\item \Fall 2009: Seminar in Django and Python at Universidad de Managua, León campus, Nicaragua.

\item \Spring 2009: Seminar in Linux, Apache, MySQL, PHP (LAMP) at Universidad de Managua, León campus, Nicaragua.

\item \Spring 2008 – \Fall 2008: English teacher at Centro de idiomas, Universidad Nacional Autonoma de Nicaragua, León campus, Nicaragua.

\item \Spring 2008: Seminar in Linux, Apache, MySQL, PHP (LAMP) at Universidad de Managua, León campus, Nicaragua.

\item \Spring 2007: International House. Teaching practice at International House, Barcelona, \Spain.

\item 2005 – 2006: Teaching internship. \english \und Social Studies, Stabekk Videregående high school, Oslo, \Norway.

\end{itemize}
